%-------------------------
% Resume in LaTeX
% Based on: https://github.com/sb2nov/resume
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Erik Pettersson} & Email: \href{mailto:erik@lazyloading.se}{erik@lazyloading.se}\\
  \href{https://www.lazyloading.se}{lazyloading.se} & Stockholm, Sweden \\
  \href{https://www.linkedin.com/in/eripet/}{linkedin.com/in/eripet} & \href{https://github.com/eripe970}{github.com/eripe970} \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
Fullstack engineer with 16+ years building scalable systems. Recently designed AI workflows and pipelines at Solva (Y Combinator). Early employee at Tink (acquired by Visa for \$2.2B), shipped backend services handling billions of requests at Apple, built Dreamwod as a solo founder. I care about both ends: clean APIs and reliable infrastructure, but also the UX details that make products enjoyable to use.

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Solva Technology — Y Combinator (S25)}{Stockholm, Sweden}
      {Founding Engineer}{Oct 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Built the full product end-to-end: UX/UI, backend, infrastructure, and security.}
        \resumeItem{Designed and implemented LLM-powered processing workflows for insurance claims automation.}
        \resumeItem{Hands-on with modern LLM tooling including prompt engineering, evaluation, and reliability.}
      \resumeItemListEnd

    \resumeSubheading
      {Apple}{Stockholm, Sweden}
      {Senior Software Engineer (Consultant)}{Oct 2022 -- Apr 2024}
      \resumeItemListStart
        \resumeItem{Individual contributor on the 3D Vision team working with raster and elevation data.}
        \resumeItem{Built, deployed, and scaled backend services in Go handling billions of requests.}
      \resumeItemListEnd

    \resumeSubheading
      {Mendi}{Stockholm, Sweden}
      {Interim Tech Lead}{Mar 2021 -- Aug 2021}
      \resumeItemListStart
        \resumeItem{Led mobile and backend development for brain health product. Managed team of 5 engineers.}
      \resumeItemListEnd

    \resumeSubheading
      {Dreamwod}{Stockholm, Sweden}
      {Founder \& Developer}{Nov 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Solo founder. Designed and built the entire product from scratch -- mobile apps, web, backend, and infrastructure.}
        \resumeItem{Used by gyms worldwide including CrossFit Munich, one of the largest CrossFit affiliates in Europe. \textasciitilde30K monthly active sessions.}
        \resumeItem{Authored technical blog with 10K+ upvotes on article "How I Built My Tech Startup as a Solo Developer".}
        \resumeItem{Tech: Go, Flutter, React, Next.js, GCP}
      \resumeItemListEnd

    \resumeSubheading
      {Stravito}{Stockholm, Sweden}
      {Tech Lead (Consultant)}{Apr 2019 -- Apr 2020}
      \resumeItemListStart
        \resumeItem{Technical leadership for architecture modernization of research and knowledge SaaS platform.}
        \resumeItem{Converted single-tenant system to multi-tenant architecture. Introduced cloud-native services and scaling patterns.}
        \resumeItem{Tech: Kotlin, Elasticsearch, Terraform, PostgreSQL, AWS}
      \resumeItemListEnd

    \resumeSubheading
      {Tink}{Stockholm, Sweden / Amsterdam, Netherlands}
      {Various roles}{Dec 2014 -- Apr 2019}
      \resumeItemListStart
        \resumeItem{Early employee (one of first 10 engineers), \#4 all-time contributor. Tink acquired by Visa for \$2.2B in 2022.}
        \resumeItem{\textbf{Tech Lead - PFM} (Jun 2018 -- Apr 2019): Led the personal finance management team.}
        \resumeItem{\textbf{Tech Lead - Payments} (Oct 2018 -- Mar 2019): Led the payments team and product.}
        \resumeItem{\textbf{Backend Chapter Lead} (Dec 2017 -- Jun 2018): Led backend developers across different teams.}
        \resumeItem{\textbf{Forward Deployed Engineer at ABN AMRO} (Jan 2016 -- Dec 2017): Forward deployed to ABN AMRO, Tink's first B2B customer. Led the white-label integration that validated the company's pivot from B2C to B2B.}
        \resumeItem{\textbf{Software Engineer} (Dec 2014 -- Jan 2016): Joined as one of the first engineers. Contributed to core platform development, product development, and reverse engineering bank integrations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Side Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Weightlifting Clinic}
      {AI-powered personal weightlifting coaching prototype. Video analysis of olympic lifts using computer vision. Tech: Go, YOLO, Flutter.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Linköping University}{Linköping, Sweden}
      {MSc in Computer Science and Engineering}{2004 -- 2009}
  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
 \begin{itemize}[leftmargin=*]
    \small{\item{
     \textbf{Languages}{: Go, Java, Kotlin, TypeScript} \\
     \textbf{Backend}{: REST APIs, Microservices, Kafka, PostgreSQL, MySQL, MongoDB, Cassandra, Elasticsearch} \\
     \textbf{Frontend/Mobile}{: React, Next.js, Flutter} \\
     \textbf{Cloud}{: AWS, GCP, Kubernetes, Terraform} \\
     \textbf{Other}{: ML/AI, LLMs, Signal Processing}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
